---
title: "BestModel"
author: "Yenan Guan"
date: "4/1/2018"
output: html_document
---

## dat4
### Data frame: all brand-specific sales quantity + region + area + KPI
```{r message = FALSE}
n = dim(corn.data)[1]
set.seed(1)
train = sample(n, 0.9*n)
attach(corn.data)
var = c("GRWR_ID", "GNSQ_FY", "BRND_DESC")
dat4 = cbind(corn.data[,var], 
             GNSQ_FYM1,
             GNSQ_sumLag,
             corn_region,
             corn_AREA_FYM1,
             corn_KPI_FYM1)
```

### Sales Quantity Prediction - Linear Regression
```{r}
lm.fit=lm(GNSQ_FY~., data = dat4[train,-which(names(dat4) == "GRWR_ID")])
lm.pred = predict(lm.fit, newdata = dat4[-train,-which(names(dat4) == "GRWR_ID")])
summary(lm.fit)$r.squared # in-sample R2
mean(lm.fit$residuals^2) # in-sample MSE
```
* in-sample
    + MSE: 2655.72
    + R-Squared: 0.5886434

```{r}
dat4$lm_pred = 0
dat4[-train, "lm_pred"] = lm.pred
mean((dat4[-train, "lm_pred"] - dat4[-train, "GNSQ_FY"])^2) # out-sample MSE, non-aggr
SST = sum((dat4[-train, "GNSQ_FY"] - mean(dat4[-train, "GNSQ_FY"]))^2)
SSE = sum((dat4[-train, "lm_pred"] - mean(dat4[-train, "GNSQ_FY"]))^2)
r.squared = SSE/SST # out-sample R2, non-aggr
r.squared 
```
* out-sample (non-aggregated)
    + MSE: 2947.72
    + R-Squared: 0.5810378

```{r}
dat.grower = dat4[-train, c("GRWR_ID", "GNSQ_FY", "lm_pred")]
dat.grower = aggregate(.~ GRWR_ID, dat.grower, sum)
mean((dat.grower$lm_pred - dat.grower$GNSQ_FY)^2) # out-sample MSE, aggr
SST = sum((dat.grower$GNSQ_FY - mean(dat.grower$GNSQ_FY))^2)
SSE = sum((dat.grower$lm_pred - mean(dat.grower$GNSQ_FY))^2)
r.squared = SSE/SST # out-sample R2, aggr
r.squared 
```
* out-sample (aggregated)
    + MSE: 3029.415
    + R-Squared: 0.582372

### Churn Prediction - Logistics Regression
```{r}
var = c("GRWR_ID", "GNSQ_FY")
dat4$purchase = 1
dat4[dat4$GNSQ_FY == 0, "purchase"] = 0
glm.fit = glm(purchase ~., data = dat4[train, -which(names(dat4) == var)], family = binomial)
glm.pred = predict(glm.fit, dat4[-train, -which(names(dat4) == var)], type = "response")
dat4$glm_pred = 0
dat4[-train, "glm_pred"] = glm.pred
dat4$pur_pred = 0
dat4[dat4$glm_pred > 0.5, "pur_pred"] = 1
mean(dat4[-train, "pur_pred"] == dat4[-train, "purchase"]) 
```
* Threshold: 0.5 - Prediction accuracy: 0.8273771

#### Confusion Matrix
```{r}
library(caret)
library(e1071)
confusionMatrix(data = as.factor(dat4[-train, "pur_pred"]), reference = as.factor(dat4[-train, "purchase"]))
```
Confusion Matrix and Statistics

Prediction |   0   |   1
---------- | ----- | ----
         0 | 18169 | 2928
         1 |  2197 | 6395
                                         
               Accuracy : 0.8274         
                 95% CI : (0.823, 0.8317)
    No Information Rate : 0.686          
    P-Value [Acc > NIR] : < 2.2e-16      
                                         
                  Kappa : 0.5906         
 Mcnemar's Test P-Value : < 2.2e-16      
                                         
            Sensitivity : 0.8921         
            Specificity : 0.6859         
         Pos Pred Value : 0.8612         
         Neg Pred Value : 0.7443         
             Prevalence : 0.6860         
         Detection Rate : 0.6120         
   Detection Prevalence : 0.7106         
      Balanced Accuracy : 0.7890         
                                         
       'Positive' Class : 0    
       
#### Analysis through a typical grower
```{r}









```






