---
title: "linear_corn(corn)"
author: "Yenan Guan"
date: "3/31/2018"
output: html_document
---

## Import File
```{r}
rm(list = ls())
library(readr)
corn.data <- read_csv("~/Downloads/Flatfile_Corn_3.30.csv")
corn.data = data.frame(corn.data)
names(corn.data)
```

delete the redundant variables
```{r}
corn.data = corn.data[, !names(corn.data) %in% c("X1", "GRWR_ADDR_CITY_NM", "GRWR_ADDR_POSTL_CD")]
```

delete the KPIs in categorical forms and delete RADL&RFM
```{r}
corn.data = corn.data[, !names(corn.data) %in% c("RADL_SCR_FY", "RADL_SCR_FYM1", "PURCH_PRBLTY_DESC_FY", "PURCH_PRBLTY_DESC_FYM1", "RFM_SCR_FY", "RFM_RANGE_FY", "RFM_SCR_FYM1", "RFM_RANGE_FYM1")]

corn.data = corn.data[, !names(corn.data) %in% c("MON_AREA_FYM2", "MON_AREA_FYM3", "MON_AREA_FYM4", "MON_AREA_FYM5", "MON_AREA_FYM6", "MON_AREA_TOTAL", "OPPO_CROP_AREA_TOTAL", "MON_AREA_FYM1_sum", "MON_AREA_FYM2_sum", "MON_AREA_FYM3_sum", "MON_AREA_FYM4_sum", "MON_AREA_FYM5_sum", "MON_AREA_FYM6_sum", "TOTAL_AREA_FYM1")]
```

delete GNSQ_sum
```{r}
corn.data = corn.data[, !names(corn.data) %in% c("GNSQ_TOTAL", "GNSQ_FYM1_sum", "GNSQ_FYM2_sum", "GNSQ_FYM3_sum", "GNSQ_FYM4_sum","GNSQ_FYM5_sum", "GNSQ_FYM6_sum")]
```

delete sales amount in dollar value
```{r}
corn.data = corn.data[, !grepl("NET_SLS_AMT_FY.*", names(corn.data))]
```

## Region
```{r}
corn.data$"IL" = 0
corn.data$"IA" = 0
corn.data$"MI/KY/IN" = 0
corn.data$"MN/WI" = 0
corn.data$"MO/KS/CO" = 0
corn.data$"ND/SD" = 0
corn.data$"NE" = 0
corn.data$"OH/NorthEastern" = 0
corn.data$"Unknown" = 0

corn.data[corn.data$GRWR_ADDR_ST_PRVNC == "IL", "IL"] = 1
corn.data[corn.data$GRWR_ADDR_ST_PRVNC == "IA", "IA"] = 1
corn.data[corn.data$GRWR_ADDR_ST_PRVNC == "MI", "MI/KY/IN"] = 1
corn.data[corn.data$GRWR_ADDR_ST_PRVNC == "KY", "MI/KY/IN"] = 1
corn.data[corn.data$GRWR_ADDR_ST_PRVNC == "IN", "MI/KY/IN"] = 1
corn.data[corn.data$GRWR_ADDR_ST_PRVNC == "MN", "MN/WI"] = 1
corn.data[corn.data$GRWR_ADDR_ST_PRVNC == "WI", "MN/WI"] = 1
corn.data[corn.data$GRWR_ADDR_ST_PRVNC == "MO", "MO/KS/CO"] = 1
corn.data[corn.data$GRWR_ADDR_ST_PRVNC == "KS", "MO/KS/CO"] = 1
corn.data[corn.data$GRWR_ADDR_ST_PRVNC == "CO", "MO/KS/CO"] = 1
corn.data[corn.data$GRWR_ADDR_ST_PRVNC == "ND", "ND/SD"] = 1
corn.data[corn.data$GRWR_ADDR_ST_PRVNC == "SD", "ND/SD"] = 1
corn.data[corn.data$GRWR_ADDR_ST_PRVNC == "NE", "NE"] = 1
corn.data[corn.data$GRWR_ADDR_ST_PRVNC == "OH", "OH/NorthEastern"] = 1
NEstates = c("CT", "DE", "ME", "MD", "MA", "NH", "NJ", "NY", "PA", "RI", "VT")
corn.data[corn.data$GRWR_ADDR_ST_PRVNC %in% NEstates, "OH/NorthEastern"] = 1 #checked from Wikipedia
corn.data[corn.data$GRWR_ADDR_ST_PRVNC == "Unknown", "Unknown"] = 1

corn.data = corn.data[, !grepl("GRWR_ADDR_ST_PRVNC", names(corn.data))]
```

## Generate other new variables - sum of FYM2-FYM6 for the certain brand and other brands
```{r}
# calculate sum of GNSQ_FYM2-FYM6
colnames(corn.data)[names(corn.data) == "GNSQ_FYM1_other"] = "GNSQ_FY16_other"
corn.data$GNSQ_sumLag_other = rowSums(corn.data[,grepl("GNSQ_FYM.*other",names(corn.data))])
corn.data = corn.data[, !grepl("GNSQ_FYM.*_other",names(corn.data))]

colnames(corn.data)[names(corn.data) == "GNSQ_FYM1"] = "GNSQ_FY16"
corn.data$GNSQ_sumLag = rowSums(corn.data[,grepl("GNSQ_FYM.*",names(corn.data))])
corn.data = corn.data[, !grepl("GNSQ_FYM.*",names(corn.data))]
colnames(corn.data)[names(corn.data) == "GNSQ_FY16"] = "GNSQ_FYM1"
colnames(corn.data)[names(corn.data) == "GNSQ_FY16_other"] = "GNSQ_FYM1_other"
```

## change the column order
```{r}
# corn.data = cbind(corn.data[c("GRWR_ID", "CROP_NM", "BRND_DESC")], corn.data[ , -which(names(corn.data) %in% c("GRWR_ID", "CROP_NM", "BRND_DESC"))])

corn.data = corn.data[, cbind("GRWR_ID", "CROP_NM", "BRND_DESC", "GNSQ_FY", "GNSQ_FYM1", "GNSQ_sumLag", "GNSQ_FYM1_other", "GNSQ_sumLag_other", "MON_AREA_FY", "MON_AREA_FYM1", "OPPO_CROP_AREA_FY", "OPPO_CROP_AREA_FYM1", "RECENCY_SCORE_FY", "RECENCY_SCORE_FYM1", "FREQUENCY_SCORE_FY", "FREQUENCY_SCORE_FYM1", "MONETARY_SCORE_FY", "MONETARY_SCORE_FYM1", "PURCH_PRBLTY_FY", "PURCH_PRBLTY_FYM1", "IL", "IA", "MI/KY/IN", "MN/WI", "MO/KS/CO", "ND/SD", "NE", "OH/NorthEastern", "Unknown" )]
names(corn.data)
```

## Categorize variables
```{r}
corn_region = corn.data[,c("IL","IA","MI/KY/IN","MN/WI","MO/KS/CO","ND/SD","NE","OH/NorthEastern","Unknown")]
corn_RFM_FYM1 = corn.data[, c("RECENCY_SCORE_FYM1", "FREQUENCY_SCORE_FYM1", "MONETARY_SCORE_FYM1")]
corn_AREA_FYM1 = corn.data[, c("MON_AREA_FYM1", "OPPO_CROP_AREA_FYM1")]
corn_KPI_FYM1 = corn.data[, c("RECENCY_SCORE_FYM1", "FREQUENCY_SCORE_FYM1", "MONETARY_SCORE_FYM1", "PURCH_PRBLTY_FYM1")]
```

# Regression: linear + logit
* Model 1: All variables
* Model 2: All variables but POP
* Model 3: one lagged year sales quantity + region + area + KPI
* **Model 4: all brand-specific sales quantity + region + area + KPI**
* Model 5: all sales quantity, no KPIs

Model | out-sample MSE | out-sample R2 | Churn_pred accuracy
----- | -------------- | ------------- | -------------------
  1   |    3029.539    |   0.5826021   |     0.8273098
  2   |    3037.443    |   0.5816021   |     0.8196638
  3   |    3083.987    |   0.577036    |     0.8269056
**4** |  **3029.415**  | **0.582372**  |   **0.8273771**
  5   |    3040.738    |   0.5797378   |     0.7855771

### preparations: set seed & specify training and test rows
```{r}
n = dim(corn.data)[1]
set.seed(1)
train = sample(n, 0.9*n)
```

## dat1
### Data frame: All variables
```{r message = FALSE}
attach(corn.data)
var = c("GRWR_ID", "GNSQ_FY", "BRND_DESC")
dat1 = cbind(corn.data[,var], 
             GNSQ_FYM1,
             GNSQ_sumLag,
             GNSQ_FYM1_other,
             GNSQ_sumLag_other,
             corn_region,
             corn_AREA_FYM1,
             corn_KPI_FYM1)
```

### Sales Quantity Prediction - Linear Regression
```{r}
lm.fit=lm(GNSQ_FY~., data = dat1[train,-which(names(dat1) == "GRWR_ID")])
lm.pred = predict(lm.fit, newdata = dat1[-train,-which(names(dat1) == "GRWR_ID")])
summary(lm.fit)$r.squared # in-sample R2
mean(lm.fit$residuals^2) # in-sample MSE
```
* in-sample
    + MSE: 2655.674
    + R-Squared: 0.5886505

```{r}
dat1$lm_pred = 0
dat1[-train, "lm_pred"] = lm.pred
mean((dat1[-train, "lm_pred"] - dat1[-train, "GNSQ_FY"])^2) # out-sample MSE, non-aggr
SST = sum((dat1[-train, "GNSQ_FY"] - mean(dat1[-train, "GNSQ_FY"]))^2)
SSE = sum((dat1[-train, "lm_pred"] - mean(dat1[-train, "GNSQ_FY"]))^2)
r.squared = SSE/SST # out-sample R2, non-aggr
r.squared 
```
* out-sample (non-aggregated)
    + MSE: 2947.681
    + R-Squared: 0.5810602

```{r}
dat.grower = dat1[-train, c("GRWR_ID", "GNSQ_FY", "lm_pred")]
dat.grower = aggregate(.~ GRWR_ID, dat.grower, sum)
mean((dat.grower$lm_pred - dat.grower$GNSQ_FY)^2) # out-sample MSE, aggr
SST = sum((dat.grower$GNSQ_FY - mean(dat.grower$GNSQ_FY))^2)
SSE = sum((dat.grower$lm_pred - mean(dat.grower$GNSQ_FY))^2)
r.squared = SSE/SST # out-sample R2, aggr
r.squared 
```
* out-sample (aggregated)
    + MSE: 3029.539
    + R-Squared: 0.5826021

### Churn Prediction - Logistics Regression
```{r}
var = c("GRWR_ID", "GNSQ_FY")
dat1$purchase = 1
dat1[dat1$GNSQ_FY == 0, "purchase"] = 0
glm.fit = glm(purchase ~., data = dat1[train, -which(names(dat1) == var)], family = binomial)
glm.pred = predict(glm.fit, dat1[-train, -which(names(dat1) == var)], type = "response")
dat1$glm_pred = 0
dat1[-train, "glm_pred"] = glm.pred
dat1$pur_pred = 0
dat1[dat1$glm_pred > 0.5, "pur_pred"] = 1
mean(dat1[-train, "pur_pred"] == dat1[-train, "purchase"]) 
```
* Threshold: 0.5 - Prediction accuracy: 0.8273098

## dat2
### Data frame: All variables but POP
```{r message = FALSE}
attach(corn.data)
var = c("GRWR_ID", "GNSQ_FY", "BRND_DESC")
dat2 = cbind(corn.data[,var], 
             GNSQ_FYM1,
             GNSQ_sumLag,
             GNSQ_FYM1_other,
             GNSQ_sumLag_other,
             corn_region,
             corn_AREA_FYM1,
             corn_RFM_FYM1)
```

### Sales Quantity Prediction - Linear Regression
```{r}
lm.fit=lm(GNSQ_FY~., data = dat2[train,-which(names(dat2) == "GRWR_ID")])
lm.pred = predict(lm.fit, newdata = dat2[-train,-which(names(dat2) == "GRWR_ID")])
summary(lm.fit)$r.squared # in-sample R2
mean(lm.fit$residuals^2) # in-sample MSE
```
* in-sample
    + MSE: 2668.692
    + R-Squared: 0.5866342

```{r}
dat2$lm_pred = 0
dat2[-train, "lm_pred"] = lm.pred
mean((dat2[-train, "lm_pred"] - dat2[-train, "GNSQ_FY"])^2) # out-sample MSE, non-aggr
SST = sum((dat2[-train, "GNSQ_FY"] - mean(dat2[-train, "GNSQ_FY"]))^2)
SSE = sum((dat2[-train, "lm_pred"] - mean(dat2[-train, "GNSQ_FY"]))^2)
r.squared = SSE/SST # out-sample R2, non-aggr
r.squared 
```
* out-sample (non-aggregated)
    + MSE: 2955.01
    + R-Squared: 0.5800302

```{r}
dat.grower = dat2[-train, c("GRWR_ID", "GNSQ_FY", "lm_pred")]
dat.grower = aggregate(.~ GRWR_ID, dat.grower, sum)
mean((dat.grower$lm_pred - dat.grower$GNSQ_FY)^2) # out-sample MSE, aggr
SST = sum((dat.grower$GNSQ_FY - mean(dat.grower$GNSQ_FY))^2)
SSE = sum((dat.grower$lm_pred - mean(dat.grower$GNSQ_FY))^2)
r.squared = SSE/SST # out-sample R2, aggr
r.squared 
```
* out-sample (aggregated)
    + MSE: 3037.443
    + R-Squared: 0.5816021

### Churn Prediction - Logistics Regression
```{r}
var = c("GRWR_ID", "GNSQ_FY")
dat2$purchase = 1
dat2[dat2$GNSQ_FY == 0, "purchase"] = 0
glm.fit = glm(purchase ~., data = dat2[train, -which(names(dat2) == var)], family = binomial)
glm.pred = predict(glm.fit, dat2[-train, -which(names(dat2) == var)], type = "response")
dat2$glm_pred = 0
dat2[-train, "glm_pred"] = glm.pred
dat2$pur_pred = 0
dat2[dat2$glm_pred > 0.5, "pur_pred"] = 1
mean(dat2[-train, "pur_pred"] == dat2[-train, "purchase"]) 
```
* Threshold: 0.5 - Prediction accuracy: 0.8196638

## dat3
### Data frame: one lagged year sales quantity + region + area + KPI
```{r message = FALSE}
attach(corn.data)
var = c("GRWR_ID", "GNSQ_FY", "BRND_DESC")
dat3 = cbind(corn.data[,var], 
             GNSQ_FYM1,
             GNSQ_FYM1_other,
             corn_region,
             corn_AREA_FYM1,
             corn_KPI_FYM1)
```

### Sales Quantity Prediction - Linear Regression
```{r}
lm.fit=lm(GNSQ_FY~., data = dat3[train,-which(names(dat3) == "GRWR_ID")])
lm.pred = predict(lm.fit, newdata = dat3[-train,-which(names(dat3) == "GRWR_ID")])
summary(lm.fit)$r.squared # in-sample R2
mean(lm.fit$residuals^2) # in-sample MSE
```
* in-sample
    + MSE: 2701.153
    + R-Squared: 0.5816061

```{r}
dat3$lm_pred = 0
dat3[-train, "lm_pred"] = lm.pred
mean((dat3[-train, "lm_pred"] - dat3[-train, "GNSQ_FY"])^2) # out-sample MSE, non-aggr
SST = sum((dat3[-train, "GNSQ_FY"] - mean(dat3[-train, "GNSQ_FY"]))^2)
SSE = sum((dat3[-train, "lm_pred"] - mean(dat3[-train, "GNSQ_FY"]))^2)
r.squared = SSE/SST # out-sample R2, non-aggr
r.squared 
```
* out-sample (non-aggregated)
    + MSE: 3000.961
    + R-Squared: 0.5753138

```{r}
dat.grower = dat3[-train, c("GRWR_ID", "GNSQ_FY", "lm_pred")]
dat.grower = aggregate(.~ GRWR_ID, dat.grower, sum)
mean((dat.grower$lm_pred - dat.grower$GNSQ_FY)^2) # out-sample MSE, aggr
SST = sum((dat.grower$GNSQ_FY - mean(dat.grower$GNSQ_FY))^2)
SSE = sum((dat.grower$lm_pred - mean(dat.grower$GNSQ_FY))^2)
r.squared = SSE/SST # out-sample R2, aggr
r.squared 
```
* out-sample (aggregated)
    + MSE: 3083.987
    + R-Squared: 0.577036

### Churn Prediction - Logistics Regression
```{r}
var = c("GRWR_ID", "GNSQ_FY")
dat3$purchase = 1
dat3[dat3$GNSQ_FY == 0, "purchase"] = 0
glm.fit = glm(purchase ~., data = dat3[train, -which(names(dat3) == var)], family = binomial)
glm.pred = predict(glm.fit, dat3[-train, -which(names(dat3) == var)], type = "response")
dat3$glm_pred = 0
dat3[-train, "glm_pred"] = glm.pred
dat3$pur_pred = 0
dat3[dat3$glm_pred > 0.5, "pur_pred"] = 1
mean(dat3[-train, "pur_pred"] == dat3[-train, "purchase"]) 
```
* Threshold: 0.5 - Prediction accuracy: 0.8269056

## dat4
### Data frame: all brand-specific sales quantity + region + area + KPI
```{r message = FALSE}
attach(corn.data)
var = c("GRWR_ID", "GNSQ_FY", "BRND_DESC")
dat4 = cbind(corn.data[,var], 
             GNSQ_FYM1,
             GNSQ_sumLag,
             corn_region,
             corn_AREA_FYM1,
             corn_KPI_FYM1)
```

### Sales Quantity Prediction - Linear Regression
```{r}
lm.fit=lm(GNSQ_FY~., data = dat4[train,-which(names(dat4) == "GRWR_ID")])
lm.pred = predict(lm.fit, newdata = dat4[-train,-which(names(dat4) == "GRWR_ID")])
summary(lm.fit)$r.squared # in-sample R2
mean(lm.fit$residuals^2) # in-sample MSE
```
* in-sample
    + MSE: 2655.72
    + R-Squared: 0.5886434

```{r}
dat4$lm_pred = 0
dat4[-train, "lm_pred"] = lm.pred
mean((dat4[-train, "lm_pred"] - dat4[-train, "GNSQ_FY"])^2) # out-sample MSE, non-aggr
SST = sum((dat4[-train, "GNSQ_FY"] - mean(dat4[-train, "GNSQ_FY"]))^2)
SSE = sum((dat4[-train, "lm_pred"] - mean(dat4[-train, "GNSQ_FY"]))^2)
r.squared = SSE/SST # out-sample R2, non-aggr
r.squared 
```
* out-sample (non-aggregated)
    + MSE: 2947.72
    + R-Squared: 0.5810378

```{r}
dat.grower = dat4[-train, c("GRWR_ID", "GNSQ_FY", "lm_pred")]
dat.grower = aggregate(.~ GRWR_ID, dat.grower, sum)
mean((dat.grower$lm_pred - dat.grower$GNSQ_FY)^2) # out-sample MSE, aggr
SST = sum((dat.grower$GNSQ_FY - mean(dat.grower$GNSQ_FY))^2)
SSE = sum((dat.grower$lm_pred - mean(dat.grower$GNSQ_FY))^2)
r.squared = SSE/SST # out-sample R2, aggr
r.squared 
```
* out-sample (aggregated)
    + MSE: 3029.415
    + R-Squared: 0.582372

### Churn Prediction - Logistics Regression
```{r}
var = c("GRWR_ID", "GNSQ_FY")
dat4$purchase = 1
dat4[dat4$GNSQ_FY == 0, "purchase"] = 0
glm.fit = glm(purchase ~., data = dat4[train, -which(names(dat4) == var)], family = binomial)
glm.pred = predict(glm.fit, dat4[-train, -which(names(dat4) == var)], type = "response")
dat4$glm_pred = 0
dat4[-train, "glm_pred"] = glm.pred
dat4$pur_pred = 0
dat4[dat4$glm_pred > 0.5, "pur_pred"] = 1
mean(dat4[-train, "pur_pred"] == dat4[-train, "purchase"]) 
```
* Threshold: 0.5 - Prediction accuracy: 0.8273771

## dat5
### Data frame: no KPIs
```{r message = FALSE}
attach(corn.data)
var = c("GRWR_ID", "GNSQ_FY", "BRND_DESC")
dat5 = cbind(corn.data[,var], 
             GNSQ_FYM1,
             GNSQ_sumLag,
             GNSQ_FYM1_other,
             GNSQ_sumLag_other,
             corn_region)
```

### Sales Quantity Prediction - Linear Regression
```{r}
lm.fit=lm(GNSQ_FY~., data = dat5[train,-which(names(dat5) == "GRWR_ID")])
lm.pred = predict(lm.fit, newdata = dat5[-train,-which(names(dat5) == "GRWR_ID")])
summary(lm.fit)$r.squared # in-sample R2
mean(lm.fit$residuals^2) # in-sample MSE
```
* in-sample
    + MSE: 2680.093
    + R-Squared: 0.5848682

```{r}
dat5$lm_pred = 0
dat5[-train, "lm_pred"] = lm.pred
mean((dat5[-train, "lm_pred"] - dat5[-train, "GNSQ_FY"])^2) # out-sample MSE, non-aggr
SST = sum((dat5[-train, "GNSQ_FY"] - mean(dat5[-train, "GNSQ_FY"]))^2)
SSE = sum((dat5[-train, "lm_pred"] - mean(dat5[-train, "GNSQ_FY"]))^2)
r.squared = SSE/SST # out-sample R2, non-aggr
r.squared 
```
* out-sample (non-aggregated)
    + MSE: 2958.257
    + R-Squared: 0.5782054

```{r}
dat.grower = dat5[-train, c("GRWR_ID", "GNSQ_FY", "lm_pred")]
dat.grower = aggregate(.~ GRWR_ID, dat.grower, sum)
mean((dat.grower$lm_pred - dat.grower$GNSQ_FY)^2) # out-sample MSE, aggr
SST = sum((dat.grower$GNSQ_FY - mean(dat.grower$GNSQ_FY))^2)
SSE = sum((dat.grower$lm_pred - mean(dat.grower$GNSQ_FY))^2)
r.squared = SSE/SST # out-sample R2, aggr
r.squared 
```
* out-sample (aggregated)
    + MSE: 3040.738
    + R-Squared: 0.5797378

### Churn Prediction - Logistics Regression
```{r}
var = c("GRWR_ID", "GNSQ_FY")
dat5$purchase = 1
dat5[dat5$GNSQ_FY == 0, "purchase"] = 0
glm.fit = glm(purchase ~., data = dat5[train, -which(names(dat5) == var)], family = binomial)
glm.pred = predict(glm.fit, dat5[-train, -which(names(dat5) == var)], type = "response")
dat5$glm_pred = 0
dat5[-train, "glm_pred"] = glm.pred
dat5$pur_pred = 0
dat5[dat5$glm_pred > 0.5, "pur_pred"] = 1
mean(dat5[-train, "pur_pred"] == dat5[-train, "purchase"]) 
```
* Threshold: 0.5 - Prediction accuracy: 0.7855771
