---
title: "linear_corn_new"
author: "Yenan Guan"
date: "4/1/2018"
output: html_document
---

## Import the latest flatfile
```{r message = FALSE}
rm(list = ls())
library(readr)
corn.data <- read_csv("~/Downloads/Flatfile_Corn_4.1.csv")
corn.data = data.frame(corn.data)
names(corn.data)
corn.data = corn.data[, !names(corn.data) %in% c("X1")]
```

## Categorize the variables
```{r}
# corn_region = corn.data[,c("IL","IA","MI_KY_IN","MN_WI","MO_KS_CO","ND_SD","NE","OH_NorthEastern_sts","Unknown")]
corn_region = corn.data[,c("IL","IA","MI_KY_IN","MN_WI","MO_KS_CO","ND_SD","NE","OH_NorthEastern_sts")]
corn_RFM_FYM1 = corn.data[, c("RECENCY_SCORE_FYM1", "FREQUENCY_SCORE_FYM1", "MONETARY_SCORE_FYM1")]
corn_AREA_FYM1 = corn.data[, c("MON_AREA_FYM1", "OPPO_CROP_AREA_FYM1")]
corn_KPI_FYM1 = corn.data[, c("RECENCY_SCORE_FYM1", "FREQUENCY_SCORE_FYM1", "MONETARY_SCORE_FYM1", "PURCH_PRBLTY_FYM1")]
```

# Regression: linear + logit
* Model 1: All variables
* Model 2: All variables but POP
* Model 3: one lagged year sales quantity + region + area + KPI
* Model 4: all brand-specific sales quantity + region + area + KPI
* Model 5: all sales quantity, no KPIs
* Model 6: all brand-specific sales quantity + other brand FY1 GNSQ + region + area + KPI
* **Model 7: (modification on model 3) lagged Monsanto area added to Model 3**

Model | out-sample MSE | out-sample R2 | Churn_pred accuracy
----- | -------------- | ------------- | -------------------
  1   |    3082.059    |   0.6805047   |     0.8263733
  2   |    3135.773    |   0.6840467   |     0.8151727
  3   |    2729.692    |   0.601388    |     0.8260056  
  4   |    2792.469    |   0.6214702   |     0.8262396 
  5   |    3090.079    |   0.6754292   |     0.7797653
  6   |    2826.43     |   0.6272803   |     0.8264068
**7** |  **2724.38**   | **0.6057023** |   **0.8259721** 

### preparations: set seed & specify training and test rows
```{r}
n = dim(corn.data)[1]
set.seed(1)
train = sample(n, 0.9*n)
```

## dat1
### Data frame: All variables
```{r message = FALSE}
attach(corn.data)
var = c("GRWR_ID", "GNSQ_FY", "BRND_DESC")
dat1 = cbind(corn.data[,var], 
             GNSQ_FYM1,
             sumLagGNSQ,
             GNSQ_FYM1_other,
             sumLagGNSQ_other,
             corn_region,
             corn_AREA_FYM1,
             corn_KPI_FYM1)
```

### Sales Quantity Prediction - Linear Regression
```{r}
lm.fit=lm(GNSQ_FY~., data = dat1[train,-which(names(dat1) == "GRWR_ID")])
lm.pred = predict(lm.fit, newdata = dat1[-train,-which(names(dat1) == "GRWR_ID")])
summary(lm.fit)$r.squared # in-sample R2
mean(lm.fit$residuals^2) # in-sample MSE
```
* in-sample
    + MSE: 2683.701
    + R-Squared: 0.5890044

```{r}
dat1$lm_pred = 0
dat1[-train, "lm_pred"] = lm.pred
mean((dat1[-train, "lm_pred"] - dat1[-train, "GNSQ_FY"])^2) # out-sample MSE, non-aggr
SST = sum((dat1[-train, "GNSQ_FY"] - mean(dat1[train, "GNSQ_FY"]))^2)
SSE = sum((dat1[-train, "lm_pred"] - mean(dat1[-train, "GNSQ_FY"]))^2)
r.squared = SSE/SST # out-sample R2, non-aggr
r.squared 
```
* out-sample (non-aggregated)
    + MSE: 2999.551
    + R-Squared: 0.6795101

```{r}
dat.grower = dat1[-train, c("GRWR_ID", "GNSQ_FY", "lm_pred")]
dat.grower = aggregate(.~ GRWR_ID, dat.grower, sum)
mean((dat.grower$lm_pred - dat.grower$GNSQ_FY)^2) # out-sample MSE, aggr
SST = sum((dat.grower$GNSQ_FY - mean(dat.grower$GNSQ_FY))^2)
SSE = sum((dat.grower$lm_pred - mean(dat.grower$GNSQ_FY))^2)
r.squared = SSE/SST # out-sample R2, aggr
r.squared 
```
* out-sample (aggregated)
    + MSE: 3082.059
    + R-Squared: 0.6805047

### Churn Prediction - Logistics Regression
```{r}
var = c("GRWR_ID", "GNSQ_FY")
dat1$purchase = 1
dat1[dat1$GNSQ_FY == 0, "purchase"] = 0
glm.fit = glm(purchase ~., data = dat1[train, -which(names(dat1) == var)], family = binomial)
glm.pred = predict(glm.fit, dat1[-train, -which(names(dat1) == var)], type = "response")
dat1$glm_pred = 0
dat1[-train, "glm_pred"] = glm.pred
dat1$pur_pred = 0
dat1[dat1$glm_pred > 0.5, "pur_pred"] = 1
mean(dat1[-train, "pur_pred"] == dat1[-train, "purchase"]) 
```
* Threshold: 0.5 - Prediction accuracy: 0.8263733

## dat2
### Data frame: All variables but POP
```{r message = FALSE}
attach(corn.data)
var = c("GRWR_ID", "GNSQ_FY", "BRND_DESC")
dat2 = cbind(corn.data[,var], 
             GNSQ_FYM1,
             sumLagGNSQ,
             GNSQ_FYM1_other,
             sumLagGNSQ_other,
             corn_region,
             corn_AREA_FYM1,
             corn_RFM_FYM1)
```

### Sales Quantity Prediction - Linear Regression
```{r}
lm.fit=lm(GNSQ_FY~., data = dat2[train,-which(names(dat2) == "GRWR_ID")])
lm.pred = predict(lm.fit, newdata = dat2[-train,-which(names(dat2) == "GRWR_ID")])
summary(lm.fit)$r.squared # in-sample R2
mean(lm.fit$residuals^2) # in-sample MSE
```
* in-sample
    + MSE: 2695.404
    + R-Squared: 0.587212

```{r}
dat2$lm_pred = 0
dat2[-train, "lm_pred"] = lm.pred
mean((dat2[-train, "lm_pred"] - dat2[-train, "GNSQ_FY"])^2) # out-sample MSE, non-aggr
SST = sum((dat2[-train, "GNSQ_FY"] - mean(dat2[train, "GNSQ_FY"]))^2)
SSE = sum((dat2[-train, "lm_pred"] - mean(dat2[-train, "GNSQ_FY"]))^2)
r.squared = SSE/SST # out-sample R2, non-aggr
r.squared 
```
* out-sample (non-aggregated)
    + MSE: 3051.95
    + R-Squared: 0.6830472

```{r}
dat.grower = dat2[-train, c("GRWR_ID", "GNSQ_FY", "lm_pred")]
dat.grower = aggregate(.~ GRWR_ID, dat.grower, sum)
mean((dat.grower$lm_pred - dat.grower$GNSQ_FY)^2) # out-sample MSE, aggr
SST = sum((dat.grower$GNSQ_FY - mean(dat.grower$GNSQ_FY))^2)
SSE = sum((dat.grower$lm_pred - mean(dat.grower$GNSQ_FY))^2)
r.squared = SSE/SST # out-sample R2, aggr
r.squared 
```
* out-sample (aggregated)
    + MSE: 3135.773
    + R-Squared: 0.6840467

### Churn Prediction - Logistics Regression
```{r}
var = c("GRWR_ID", "GNSQ_FY")
dat2$purchase = 1
dat2[dat2$GNSQ_FY == 0, "purchase"] = 0
glm.fit = glm(purchase ~., data = dat2[train, -which(names(dat2) == var)], family = binomial)
glm.pred = predict(glm.fit, dat2[-train, -which(names(dat2) == var)], type = "response")
dat2$glm_pred = 0
dat2[-train, "glm_pred"] = glm.pred
dat2$pur_pred = 0
dat2[dat2$glm_pred > 0.5, "pur_pred"] = 1
mean(dat2[-train, "pur_pred"] == dat2[-train, "purchase"]) 
```
* Threshold: 0.5 - Prediction accuracy: 0.8151727

## dat3
### Data frame: one lagged year sales quantity + region + area + KPI
```{r message = FALSE}
attach(corn.data)
var = c("GRWR_ID", "GNSQ_FY", "BRND_DESC")
dat3 = cbind(corn.data[,var], 
             GNSQ_FYM1,
             GNSQ_FYM1_other,
             corn_region,
             corn_AREA_FYM1,
             corn_KPI_FYM1)
```

### Sales Quantity Prediction - Linear Regression
```{r}
lm.fit=lm(GNSQ_FY~., data = dat3[train,-which(names(dat3) == "GRWR_ID")])
lm.pred = predict(lm.fit, newdata = dat3[-train,-which(names(dat3) == "GRWR_ID")])
summary(lm.fit)$r.squared # in-sample R2
mean(lm.fit$residuals^2) # in-sample MSE
```
* in-sample
    + MSE: 2748.183
    + R-Squared: 0.5791293

```{r}
dat3$lm_pred = 0
dat3[-train, "lm_pred"] = lm.pred
mean((dat3[-train, "lm_pred"] - dat3[-train, "GNSQ_FY"])^2) # out-sample MSE, non-aggr
SST = sum((dat3[-train, "GNSQ_FY"] - mean(dat3[train, "GNSQ_FY"]))^2)
SSE = sum((dat3[-train, "lm_pred"] - mean(dat3[-train, "GNSQ_FY"]))^2)
r.squared = SSE/SST # out-sample R2, non-aggr
r.squared 
```
* out-sample (non-aggregated)
    + MSE: 2657.931
    + R-Squared: 0.6000323

```{r}
dat.grower = dat3[-train, c("GRWR_ID", "GNSQ_FY", "lm_pred")]
dat.grower = aggregate(.~ GRWR_ID, dat.grower, sum)
mean((dat.grower$lm_pred - dat.grower$GNSQ_FY)^2) # out-sample MSE, aggr
SST = sum((dat.grower$GNSQ_FY - mean(dat.grower$GNSQ_FY))^2)
SSE = sum((dat.grower$lm_pred - mean(dat.grower$GNSQ_FY))^2)
r.squared = SSE/SST # out-sample R2, aggr
r.squared 
```
* out-sample (aggregated)
    + MSE: 2729.692
    + R-Squared: 0.601388

### Churn Prediction - Logistics Regression
```{r}
var = c("GRWR_ID", "GNSQ_FY")
dat3$purchase = 1
dat3[dat3$GNSQ_FY == 0, "purchase"] = 0
glm.fit = glm(purchase ~., data = dat3[train, -which(names(dat3) == var)], family = binomial)
glm.pred = predict(glm.fit, dat3[-train, -which(names(dat3) == var)], type = "response")
dat3$glm_pred = 0
dat3[-train, "glm_pred"] = glm.pred
dat3$pur_pred = 0
dat3[dat3$glm_pred > 0.5, "pur_pred"] = 1
mean(dat3[-train, "pur_pred"] == dat3[-train, "purchase"]) 
```
* Threshold: 0.5 - Prediction accuracy: 0.8260056

## dat4
### Data frame: all brand-specific sales quantity + region + area + KPI
```{r message = FALSE}
attach(corn.data)
var = c("GRWR_ID", "GNSQ_FY", "BRND_DESC")
dat4 = cbind(corn.data[,var], 
             GNSQ_FYM1,
             sumLagGNSQ,
             corn_region,
             corn_AREA_FYM1,
             corn_KPI_FYM1)
```

### Sales Quantity Prediction - Linear Regression
```{r}
lm.fit=lm(GNSQ_FY~., data = dat4[train,-which(names(dat4) == "GRWR_ID")])
lm.pred = predict(lm.fit, newdata = dat4[-train,-which(names(dat4) == "GRWR_ID")])
summary(lm.fit)$r.squared # in-sample R2
mean(lm.fit$residuals^2) # in-sample MSE
```
* in-sample
    + MSE: 2724.536
    + R-Squared: 0.5827506

```{r}
dat4$lm_pred = 0
dat4[-train, "lm_pred"] = lm.pred
mean((dat4[-train, "lm_pred"] - dat4[-train, "GNSQ_FY"])^2) # out-sample MSE, non-aggr
SST = sum((dat4[-train, "GNSQ_FY"] - mean(dat4[train, "GNSQ_FY"]))^2)
SSE = sum((dat4[-train, "lm_pred"] - mean(dat4[-train, "GNSQ_FY"]))^2)
r.squared = SSE/SST # out-sample R2, non-aggr
r.squared 
```
* out-sample (non-aggregated)
    + MSE: 2720.469
    + R-Squared: 0.6175926

```{r}
dat.grower = dat4[-train, c("GRWR_ID", "GNSQ_FY", "lm_pred")]
dat.grower = aggregate(.~ GRWR_ID, dat.grower, sum)
mean((dat.grower$lm_pred - dat.grower$GNSQ_FY)^2) # out-sample MSE, aggr
SST = sum((dat.grower$GNSQ_FY - mean(dat.grower$GNSQ_FY))^2)
SSE = sum((dat.grower$lm_pred - mean(dat.grower$GNSQ_FY))^2)
r.squared = SSE/SST # out-sample R2, aggr
r.squared 
```
* out-sample (aggregated)
    + MSE: 2792.469
    + R-Squared: 0.6214702

### Churn Prediction - Logistics Regression
```{r}
var = c("GRWR_ID", "GNSQ_FY")
dat4$purchase = 1
dat4[dat4$GNSQ_FY == 0, "purchase"] = 0
glm.fit = glm(purchase ~., data = dat4[train, -which(names(dat4) == var)], family = binomial)
glm.pred = predict(glm.fit, dat4[-train, -which(names(dat4) == var)], type = "response")
dat4$glm_pred = 0
dat4[-train, "glm_pred"] = glm.pred
dat4$pur_pred = 0
dat4[dat4$glm_pred > 0.5, "pur_pred"] = 1
mean(dat4[-train, "pur_pred"] == dat4[-train, "purchase"]) 
```
* Threshold: 0.5 - Prediction accuracy: 0.8262396

## dat5
### Data frame: no KPIs
```{r message = FALSE}
attach(corn.data)
var = c("GRWR_ID", "GNSQ_FY", "BRND_DESC")
dat5 = cbind(corn.data[,var], 
             GNSQ_FYM1,
             sumLagGNSQ,
             GNSQ_FYM1_other,
             sumLagGNSQ_other,
             corn_region)
```

### Sales Quantity Prediction - Linear Regression
```{r}
lm.fit=lm(GNSQ_FY~., data = dat5[train,-which(names(dat5) == "GRWR_ID")])
lm.pred = predict(lm.fit, newdata = dat5[-train,-which(names(dat5) == "GRWR_ID")])
summary(lm.fit)$r.squared # in-sample R2
mean(lm.fit$residuals^2) # in-sample MSE
```
* in-sample
    + MSE: 2699.109
    + R-Squared: 0.5866447

```{r}
dat5$lm_pred = 0
dat5[-train, "lm_pred"] = lm.pred
mean((dat5[-train, "lm_pred"] - dat5[-train, "GNSQ_FY"])^2) # out-sample MSE, non-aggr
SST = sum((dat5[-train, "GNSQ_FY"] - mean(dat5[train, "GNSQ_FY"]))^2)
SSE = sum((dat5[-train, "lm_pred"] - mean(dat5[-train, "GNSQ_FY"]))^2)
r.squared = SSE/SST # out-sample R2, non-aggr
r.squared 
```
* out-sample (non-aggregated)
    + MSE: 3007.202
    + R-Squared: 0.6744156

```{r}
dat.grower = dat5[-train, c("GRWR_ID", "GNSQ_FY", "lm_pred")]
dat.grower = aggregate(.~ GRWR_ID, dat.grower, sum)
mean((dat.grower$lm_pred - dat.grower$GNSQ_FY)^2) # out-sample MSE, aggr
SST = sum((dat.grower$GNSQ_FY - mean(dat.grower$GNSQ_FY))^2)
SSE = sum((dat.grower$lm_pred - mean(dat.grower$GNSQ_FY))^2)
r.squared = SSE/SST # out-sample R2, aggr
r.squared 
```
* out-sample (aggregated)
    + MSE: 3090.079
    + R-Squared: 0.6754292

### Churn Prediction - Logistics Regression
```{r}
var = c("GRWR_ID", "GNSQ_FY")
dat5$purchase = 1
dat5[dat5$GNSQ_FY == 0, "purchase"] = 0
glm.fit = glm(purchase ~., data = dat5[train, -which(names(dat5) == var)], family = binomial)
glm.pred = predict(glm.fit, dat5[-train, -which(names(dat5) == var)], type = "response")
dat5$glm_pred = 0
dat5[-train, "glm_pred"] = glm.pred
dat5$pur_pred = 0
dat5[dat5$glm_pred > 0.5, "pur_pred"] = 1
mean(dat5[-train, "pur_pred"] == dat5[-train, "purchase"]) 
```
* Threshold: 0.5 - Prediction accuracy: 0.7797653


## dat6
### Data frame: no KPIs
```{r message = FALSE}
attach(corn.data)
var = c("GRWR_ID", "GNSQ_FY", "BRND_DESC")
dat6 = cbind(corn.data[,var], 
             GNSQ_FYM1,
             sumLagGNSQ,
             GNSQ_FYM1_other,
             corn_region,
             corn_AREA_FYM1,
             corn_KPI_FYM1)
```

### Sales Quantity Prediction - Linear Regression
```{r}
lm.fit=lm(GNSQ_FY~., data = dat6[train,-which(names(dat6) == "GRWR_ID")])
lm.pred = predict(lm.fit, newdata = dat6[-train,-which(names(dat6) == "GRWR_ID")])
summary(lm.fit)$r.squared # in-sample R2
mean(lm.fit$residuals^2) # in-sample MSE
```
* in-sample
    + MSE: 2717.09
    + R-Squared: 0.583891

```{r}
dat6$lm_pred = 0
dat6[-train, "lm_pred"] = lm.pred
mean((dat6[-train, "lm_pred"] - dat6[-train, "GNSQ_FY"])^2) # out-sample MSE, non-aggr
SST = sum((dat6[-train, "GNSQ_FY"] - mean(dat6[train, "GNSQ_FY"]))^2)
SSE = sum((dat6[-train, "lm_pred"] - mean(dat6[-train, "GNSQ_FY"]))^2)
r.squared = SSE/SST # out-sample R2, non-aggr
r.squared 
```
* out-sample (non-aggregated)
    + MSE: 2753.268
    + R-Squared: 0.6257004

```{r}
dat.grower = dat6[-train, c("GRWR_ID", "GNSQ_FY", "lm_pred")]
dat.grower = aggregate(.~ GRWR_ID, dat.grower, sum)
mean((dat.grower$lm_pred - dat.grower$GNSQ_FY)^2) # out-sample MSE, aggr
SST = sum((dat.grower$GNSQ_FY - mean(dat.grower$GNSQ_FY))^2)
SSE = sum((dat.grower$lm_pred - mean(dat.grower$GNSQ_FY))^2)
r.squared = SSE/SST # out-sample R2, aggr
r.squared 
```
* out-sample (aggregated)
    + MSE: 2826.43
    + R-Squared: 0.6272803

### Churn Prediction - Logistics Regression
```{r}
var = c("GRWR_ID", "GNSQ_FY")
dat6$purchase = 1
dat6[dat6$GNSQ_FY == 0, "purchase"] = 0
glm.fit = glm(purchase ~., data = dat6[train, -which(names(dat6) == var)], family = binomial)
glm.pred = predict(glm.fit, dat6[-train, -which(names(dat6) == var)], type = "response")
dat6$glm_pred = 0
dat6[-train, "glm_pred"] = glm.pred
dat6$pur_pred = 0
dat6[dat6$glm_pred > 0.5, "pur_pred"] = 1
mean(dat6[-train, "pur_pred"] == dat6[-train, "purchase"]) 
```
* Threshold: 0.5 - Prediction accuracy: 0.8264068

## dat7
### Data frame: one lagged year sales quantity + region + area + KPI + lagged Monsanto area
```{r message = FALSE}
attach(corn.data)
var = c("GRWR_ID", "GNSQ_FY", "BRND_DESC")
dat7 = cbind(corn.data[,var], 
             GNSQ_FYM1,
             GNSQ_FYM1_other,
             corn_region,
             corn_AREA_FYM1,
             sumLagMON_AREA,
             corn_KPI_FYM1)
```

### Sales Quantity Prediction - Linear Regression
```{r}
lm.fit=lm(GNSQ_FY~., data = dat7[train,-which(names(dat7) == "GRWR_ID")])
lm.pred = predict(lm.fit, newdata = dat7[-train,-which(names(dat7) == "GRWR_ID")])
summary(lm.fit)$r.squared # in-sample R2
mean(lm.fit$residuals^2) # in-sample MSE
```
* in-sample
    + MSE: 2731.524
    + R-Squared: 0.5816805

```{r}
dat7$lm_pred = 0
dat7[-train, "lm_pred"] = lm.pred
mean((dat7[-train, "lm_pred"] - dat7[-train, "GNSQ_FY"])^2) # out-sample MSE, non-aggr
SST = sum((dat7[-train, "GNSQ_FY"] - mean(dat7[train, "GNSQ_FY"]))^2)
SSE = sum((dat7[-train, "lm_pred"] - mean(dat7[-train, "GNSQ_FY"]))^2)
r.squared = SSE/SST # out-sample R2, non-aggr
r.squared 
```
* out-sample (non-aggregated)
+ MSE: 2652.492
+ R-Squared: 0.6043924

```{r}
dat.grower = dat7[-train, c("GRWR_ID", "GNSQ_FY", "lm_pred")]
dat.grower = aggregate(.~ GRWR_ID, dat.grower, sum)
mean((dat.grower$lm_pred - dat.grower$GNSQ_FY)^2) # out-sample MSE, aggr
SST = sum((dat.grower$GNSQ_FY - mean(dat.grower$GNSQ_FY))^2)
SSE = sum((dat.grower$lm_pred - mean(dat.grower$GNSQ_FY))^2)
r.squared = SSE/SST # out-sample R2, aggr
r.squared 
```
* out-sample (aggregated)
+ MSE: 2724.38
+ R-Squared: 0.6057023

### Churn Prediction - Logistics Regression
```{r}
var = c("GRWR_ID", "GNSQ_FY")
dat7$purchase = 1
dat7[dat7$GNSQ_FY == 0, "purchase"] = 0
glm.fit = glm(purchase ~., data = dat7[train, -which(names(dat7) == var)], family = binomial)
glm.pred = predict(glm.fit, dat7[-train, -which(names(dat7) == var)], type = "response")
dat7$glm_pred = 0
dat7[-train, "glm_pred"] = glm.pred
dat7$pur_pred = 0
dat7[dat7$glm_pred > 0.5, "pur_pred"] = 1
mean(dat7[-train, "pur_pred"] == dat7[-train, "purchase"]) 
```
* Threshold: 0.5 - Prediction accuracy: 0.8259721

